A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-09-19 paper/paper.discussion.tex
Work on methods fixes

In our simulations, we also found that increasing the number of requests per
clinician did not affect the runtime of the algorithm, highlighting the
flexibility of the tool to incorporate clinician preferences. Further, we saw
that the algorithm can accommodate an increase in time-horizon up to four years
with little impact on runtime, suggesting the algorithm can be used generate
schedules far in advance. One key limitation we identified was the sensitivity
of the runtime to larger numbers of services offered by a single department.
Such cases are unlikely to be encountered in the real-world because most
clinical departments tend to provide a single service or at most two services by
the same roster of clinicians [{\color{red}SM/Kevin, could you help with
	reference here?}]. One solution to mitigate the runtime issues created by a
larger number of services would be relaxing the constraints that prevent
assignment of consecutive blocks, followed by manual readjustment from the
generated schedule. %what do we mean by certain constraints? specify the other
%constraints?
Overall, our sensitivity analyses using simulated data provided reassurance that
the ILP formulation can be applied to schedule clinicians across real-world
variability between clinical departments. %SM - will look for reference and we
%can ask Kevin Gough too.
Next steps include expanding the generalizability of the tool beyond smaller
clinical departments to larger departments within and outside of health-care --
especially those that provide multiple services in parallel for patients and
other clients.

>>>>

In our simulations, we also found that increasing the number of requests per
clinician did not affect the runtime of the algorithm, highlighting the
flexibility of the tool to incorporate clinician preferences. Further, we saw
that the algorithm can accommodate an increase in time-horizon up to four years
with little impact on runtime, suggesting the algorithm can be used generate
schedules far in advance. One key limitation we identified was the sensitivity
of the runtime to larger numbers of services offered by a single department.
Such cases are unlikely to be encountered in the real-world because most
clinical departments tend to provide a single service or at most two services by
the same roster of clinicians [{\color{red}SM/Kevin, could you help with
	reference here?}]. One solution to mitigate the runtime issues created by a
larger number of services would be removing the constraints that prevent
assignment of consecutive blocks, followed by manual readjustment from the
generated schedule. %what do we mean by certain constraints? specify the other
%constraints?
Overall, our sensitivity analyses using simulated data provided reassurance that
the ILP formulation can be applied to schedule clinicians across real-world
variability between clinical departments. %SM - will look for reference and we
%can ask Kevin Gough too.
Next steps include expanding the generalizability of the tool beyond smaller
clinical departments to larger departments within and outside of health-care --
especially those that provide multiple services in parallel for patients and
other clients.
